% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
%\pagenumbering{gobble} % suppress displaying page number

\name{Hou Liang}

\basicInfo{
  \email{1306715855@@qq.com} \textperiodcentered\ 
  \phone{(+86) 177-586-89103} \textperiodcentered 
  }

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Tongji University (TJU)}, Shanghai, China}{2020 -- Present}
\textit{B.S.} in Software Engineering (SE), expected July 2024
\begin{itemize}
  \item \textbf{Core Modules: }Software Testing, Database Principles and Applications, Mathematical Analysis, Optimization Theory, Operating Systems, Computer Network, Software Design Patterns
  \item \textbf{GPA: }4.06/5.00 (85.58/100)
\end{itemize}


\section{\faUsers\ Work Experience}
\datedsubsection{\textbf{Shanghai Yunna Information Technology Co., Ltd.} Shanghai, China}{Jun. 2023 -- Present}
\role{Backend Developer}{Intern}
\begin{itemize}
  \item Responsible for daily maintenance, modification, and updating of post-processing code to ensure system compatibility with new testing data.
  \item Developed new features for an annotation tool used in preparing data for training an image recognition model. This involved creating a front-end page using the React framework and integrating it with an OCR API to retrieve results, enabling users to visually annotate objects.
  \item Conducted image recognition model training using Alibaba Cloud: Generated an experimental report with insights on recall rate, model parameters, precision rate, in-depth examination of error cases, and recommendations for enhancement.
  \item Performed API testing for a backend project: Developed a Python testing script with multiple rules for calculating pass rates across all testing files and provided detailed error reports, including file names and issue descriptions.
\end{itemize}

\datedsubsection{\textbf{Tongji University School of Transportation Onsite Project}}{Jan. 2023 -- Aug. 2023}
\role{Backend Developer}{Research Project}
\begin{itemize}
  \item Participated in the entire lifecycle of developing a website from scratch. Designed and developed APIs for Onsite system based on Spring boot, effectively integrating it with MyBatis.
  \item Reviewed and edited the project’s illustration document, which included project schematics and specifications for developing new APIs.
  \item Refactored the data framework and optimized concurrent performance.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faUsers\ Other Experience}
\begin{itemize}[parsep=0.5ex]
  \item Served as the team leader for a 10-member group in a practical project for the Database course, coordinating the work of various developers and achieving an ’A’ grade.
  \item Served as a mezzo-soprano in the Tongji University Student Choir, participating in performances for the school’s graduation ceremony and various other events.
  \item Worked as a part-time one-on-one tutor at Miao Companion Education Institution, providing mathematics instruction to a fifth-grade student in Shanghai.
  \item Volunteered with the College Student Ecological Civilization Service Team, delivering instructional sessions on Garbage Sorting at Hongkou District Foreign Language Primary School in Shanghai, China.
\end{itemize}

\section{\faHeartO\ Honors / Awards}
\begin{itemize}[parsep=0.5ex]
  \item {\textit{Outstanding Prize}, Award on Tongji University Freshman Cup Autonomous Driving Car Competition }{Mar. 2021}
  \item {\textit{Outstanding Prize}, Award on Tongji University Mathematical Modeling Competition }{May. 2022}
\end{itemize}

\section{\faCogs\ Skills / Interests}
\begin{itemize}[parsep=0.5ex]
  \item Language: English (fluent), Chinese (native)
  \item Programming Languages: C, Python, C++, Java
  \item IT Skills: Linux, Pycharm, Intell iJ, Git
  \item Interests: Yoga, reading, jogging, writing
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
